%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anubhav Ujjawal} % Your name
\address{\href{mailto:anubhav.u16@iiits.in}{anubhav.u16@iiits.in}, \href{mailto:anubhavujjawal@gmail.com}{anubhavujjawal@gmail.com}}
\address{(+91)7550130647} % Your phone number and email
%\address{Ramana Road, Gaya, Bihar 823001} % Your address

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Information Technology, Sri City} \hfill {\em August 2016 - Present} 
\\ Junior Undergraduate \hfill { CGPA: 8.7/10}
\\ Department of Computer Science and Engineering  
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages  &  C/C++, Python, JavaScript, Dart, LaTex, HTML \\
Frameworks \& Databases & Django, Vue.js, React.js, jQuery, Bootstrap, Dialogflow, \\ & MongoDB, SQL, Flutter, ExpressJS \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{IIIT Sri City}{August 2018 - December 2018}{Undergraduate Teaching Assistant}{}
\item Assisted the course instructor during the lab and tutorial sessions of ``Overview of Computers" Course. 
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{SSS Web Research}{2017 - Current}{Full Stack Developer}{}
\item Worked with a team of 7 people and did rapid development of ERP systems for educational institutions.
\item Built on a report generator to generate reports of performance, attendance, basic information of students.
\item Created a panel for smooth handling of Examinations in the institutions, from creation of exams to assigning marks to students and publishing the results.
\item Worked on other crucial functionalities such as library management, attendance, assignments and others.
\end{rSubsection}

\begin{rSubsection}{EaseAssist Solutions Limited}{June 2017 - July 2017}{Backend Developer Intern}{}
\item Worked on the product, Refier and integrated OAuth2 login methods.
\item Used django-notify-x to add a notification system for their system. Used Observable pattern to send notifications to the users. 
\item Wrote code to import and export data from excel sheets into the database, and handle errors as well.
\item Used \textit{Django-haystack} with Elasticsearch and integrated modular search for some parts of the system.
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Achievements} \itemsep -2pt
\item Won $1^{st}$ prize in TopBot (a chatbot making event), $2^{nd}$ prize in MedTech Hackathon (A Machine Learning based Hackathon), $3^{rd}$ prize in Appathon in Techfesia 2018.
\item Volunteered to create the Techfesia 2018 mobile app, which went on to become the $6^{th}$ most trending app in the events category.
%\item Gave multiple talks on behalf of Gradient, programming club of IIITS on web development topics. 
\item Became the $1^{st}$ development head of Gradient, programming club of IIITS.  
\item Rewarded with a paid domain for a year from \textit{Codechef} for qualifying in eliminator round of SnackDown
2017.
\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Relevant Courses}
% \itab{\textbf{Core Courses}} \tab{}  \tab{\textbf{Other Courses}}
% \\ \itab{Fluid Mechanics \& its applications } \tab{}  \tab{Computational Methods in Engineering}
% \\ \itab{Thermodynamics} \tab{}  \tab{Fundamental of Computing} 
% \\ \itab{Heat Transfer \& its applications} \tab{}  \tab{Probability and Statistics} 
% \\ \itab{Mass Transfer \& its applications} \tab{} \tab{Calculus \& Linear Algebra}
% \\ \itab{Transport Phenomena (ongoing)} \tab{} \tab{Introduction to Mechanics}
% % \\ \itab{Process Control (ongoing)} \tab{} \tab{Electrodynamics}

% \end{rSection}
\begin{rSection}{PROJECTS}

\begin{rSubsection}{\href{https://github.com/anuragiiits/Water-Management-System}{Water Management System for Plants}}{}{}{}
\item The project features a Water Management System using Raspberry Pi and Arduino along with sensors for monitoring the plants. 
\item It allowed automatic/manual and efficient watering of the plants, depending on the current condition of soil, plants and weather, from a web based dashboard or a web-view in mobile app.
\end{rSubsection}

\begin{rSubsection}{\href{https://github.com/AnubhavUjjawal/dbmsMini-1}{Subtitles sharing Web application}}{}{}{}
\item The project features a subtitles sharing website like \href{https://www.yifysubtitles.com/}{Yify Subtitles}. 
\item Used MySQL with Express.js and its middlewares as backend, Bootstrap as front-end. Used passport.js with Google OAuth for Authentication.
\end{rSubsection}

\begin{rSubsection}{\href{https://www.amazon.in/Anubhav-Ujjawal-Latest-HackerNews-Articles/dp/B07K1X4WXW}{Alexa Skills Developer}, \href{https://assistant.google.com/services/a/uid/000000b6cb59ef4f?hl=en-GB}{Google Actions Developer}}{}{}{}
\item Developed Alexa Skills and Google actions to get free credits and T-Shirt on AWS and GCP and more importantly, have some fun. 
\end{rSubsection}
\end{rSection}




\begin{rSection}{POSITION OF RESPONSIBILITY}

\begin{rSubsection}{Techfesia 2018}{June 2018 - September 2018}{App Development and Support}{IIIT Sri City}
\item Spearheaded a team of 10 people to successfully create the Techfesia website and app.
\item Managed the database, Django server and added cron jobs for sending notifications to the participants.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Development Head, Gradient}{}{}{}
\item Coordinating with Gradient's committee and planning internal events and talks for $1^{st}$ and $2^{nd}$ year students.
\item Organized sessions on Web Development and App Development for over 100 students. 
\end{rSubsection}

%------------------------------------------------

\end{rSection}

%----------------------------------------------------------------------------------------
% \begin{rSection}{Extra-Cirrucular} \itemsep -3pt
% \item Secured Gold in M.P. State Throw Ball competition and represented district in State Hand Ball competition
% \item Represented Institute in Udghosh’13 and secured second prize in Kho-Kho intramurals
% \item Secured second prize in Dance Drama competition in Galaxy’14, inter hall cultural competition of IIT Kanpur
% \item Won second prize in Electromania, circuit game designing competition in Takneek’13, inter hall technical festival of IIT Kanpur
 % \item Member, Athletics Team, IIT Kanpur. Attended Summer Sport Camp as a long jumper.
%\item Trained and disciplined in National Cadet Corps (NCC), IIT Kanpur for a year.
 %\item  Participated in Vijyoshi Camp 2012 organized at Indian Institute of Science, Bangalore.
 %\item Won 2nd position in Kho-Kho in Intramurals conducted by Physical Education Section, IIT Kanpur.
 %\item Pursued French as second language during secondary school from Grade 6 to Grade 10. Also participated in French Song Competition and French G.K. Quiz in Class 10th. %

% \end{rSection}

\end{document}
